Combinatorics of the geometry of Wilson loop diagrams

### 2019-02-06 General WLD combinatorics.tex
take 2 on inside and outside

@@

\begin{dfn}\label{props inside p}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $\vec{p} = (i,j) \in \cP$ be a directional propagator and $\cev{p} = (j,i)$ be the same propagator with the opposite directionality. Call the vertices of $W$ \bas V_{in}(\vec{p}) = \{a \in [n] | i <_i a <_i j\} \cup V(p) \eas the region of $W$ {\bf inside} $\vec{p}$, and \bas V_{out}(\vec{p}) = \{a \in [n] | j <_j a <_j i\} \cup V(p) \;.\eas the region {\bf outside }$\vec{p}$. The set of propagators inside (resp. outside) $\vec{p}$ are those lying in the region inside (resp. outside) are the $q \neq p \in \cP$ such that  $V(q) \subset V_{in}(p)$ (resp. $V(q) \subset V_{out}(p)$) .
\end{dfn}

Note that under this definiton, $V_{in}(\vec{p}) = V_{out}(\cev{p})$ and $V_{out}(\vec{p}) = V_{in}(\cev{p})$. That is, the regions inside and outside of a propagator switch depending on the direction imposed on the propagators $p$.

\begin{dfn}\note{right now this doesn't depend on the order of $i$ and $j$, but that might matter later on?}
Let $p = (i,j) \in cP$ be a propagator in $W$.  Define the \textit{length} of $p$ to be 
\[\ell(p) = min\big\{|V_(in)(\vec{p})|,|V_(in)(\cev{p})|\big\}-2 = min\big\{|[i+1,j]|,|[j+1,i]|\big\}.\]
\end{dfn}
In other words, given that $p$ partitions the vertices of $W$, $\ell(p)$ is the size of the smaller of the two partitions.

>>>>

Note that for any Wilson loop diagram, $W = (\cP, n)$, each propagator $P$ partions $n$ into two sets, $\{V_{in}(p), V_{out}(p)\}$, where $V_{in}(p)$ and $V_{out}(p)$ correspond to the two  cyclic subintervals of $[n]$ that lie on either side of $p$. This in turn defines three sets of propagators, $\{\cP_{in}, p, \cP_{out}\}$, where (for $\bullet \in \{in, \; out\}$) \bas \cP_{\bullet} = \{ q \in (\cP \setminus p) | V(q) \cap V_{\bullet}(p)  \neq \emptyset \} \;.\eas If $W$ has no propagators crossing $p$ and no other propagator supported on $V(p)$, then the set $\{\cP_{in}, p, \cP_{out}\}$ partitions $\cP$. The set $\cP_{in}$ defines the propagators with end points on one side of $p$, while $\cP_{out}$ defines the propagators with end points on the other side. In particular, for (weakly) admissible Wilson loop diagrams, the set $\{\cP_{in}, p, \cP_{out}\}$ is a partition for every propagators $p \in \cP$.

It remains to determine with set of propagators/vertices are refered to as on the inside of $p$ and which are on the outside. To do this, we impose a direction on $p$.

@@

\begin{dfn}\label{props inside p}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram, with $p = (i,j) \in \cP$. Write $(p, <_i)$ be the same propagator with a direction induced by the linear ordering $<_i$. Then \bas V_{in}(p, <_i) = \{a \in [n] | i+1 <_i a <_i j \}\eas the region of $W$ {\bf inside} $p$, and \bas V_{out}(p, <_i) = \{a \in [n] | j+1 <_j a <_j i \} \;.\eas the region {\bf outside }$p$. 
\end{dfn}

We may associate the propagators on the inside and outside of $p$ accordingly.

Note that under this definiton, $V_{in}(p, <_i) = V_{out}(p, <_j)$. That is, which set of propagators lie inside and outside of $p$ switch depending on the direction imposed $p$.

\begin{dfn}\note{right now this doesn't depend on the order of $i$ and $j$, but that might matter later on?}
Let $p = (i,j) \in cP$ be a propagator in $W$.  Define the \textit{length} of $p$ to be 
\[\ell(p) = min\big\{|V_{in}(p)|,|V_{out}(p)|\big\} = min\big\{|[i+1,j]|,|[j+1,i]|\big\}.\]
\end{dfn}
In other words, $\ell(p)$ is the size of the smaller of the two sets $V_{in}(p)$ and $V_{out}(p)$ defined above.
